Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-06-04 paper/main.tex
Data for benchmark functions
Author and acknowledgements

% Added by wenlong lyu
\usepackage{amsmath}
\usepackage[plain]{fancyref}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{placeins}

@@

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

@@

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

@@

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

>>>>

% Added by wenlong lyu
\usepackage{amsmath}
\usepackage[plain]{fancyref}
\usepackage{bm}
\usepackage{todonotes}
\usepackage{placeins}
\usepackage{multirow}

@@

% % Use the following line for the initial blind version submitted for review:
% \usepackage{icml2018}

% If accepted, instead use the following line for the camera-ready submission:
\usepackage[accepted]{icml2018}

@@

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
% \icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
    \icmlauthor{Wenlong Lyu}{fudan}
    \icmlauthor{Fan Yang}{fudan}
    \icmlauthor{Changhao Yan}{fudan}
    \icmlauthor{Dian Zhou}{fudan,utd}
    \icmlauthor{Xuan Zeng}{fudan}
% \icmlauthor{Aeiau Zzzz}{equal,to}
% \icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
% \icmlauthor{Cieua Vvvvv}{goo}
% \icmlauthor{Iaesut Saoeu}{ed}
% \icmlauthor{Fiuea Rrrr}{to}
% \icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
% \icmlauthor{Aaoeu Iasoh}{goo}
% \icmlauthor{Buiui Eueu}{ed}
% \icmlauthor{Aeuia Zzzz}{ed}
% \icmlauthor{Bieea C.~Yyyy}{to,goo}
% \icmlauthor{Teoau Xxxx}{ed}
% \icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

% \icmlaffiliation{utd}{utdallas}
\icmlaffiliation{fudan}{State Key Lab of ASIC and System, Microelectronics Department, Fudan University, China}
\icmlaffiliation{utd}{Department of Electrical Engineering, University of Texas at Dallas, Richardson, TX, U.S.A}
% \icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
% \icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
% \icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Xuan Zeng}{xzeng@fudan.edu.cn}
% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

@@

\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
% \printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

@@

\section*{Acknowledgements}
This research was supported  partly by the National Major Science and
Technology Special Project of China (2017ZX01028101-003), partly by National
Natural Science Foundation of China (NSFC) research projects 61774045,
61574044, 61474026, 61574046, 61674042, and 61628402 and partly by the
Recruitment Program of Global Experts (the Thousand Talents Plan).

aaaa
